Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-05-10 doc/RMD/mlg-mcg.Rmd
add visNetwork
need to work on the presentation, but that can be
done later

```{r load_packages}
library('igraph')
library('ggraph')
library('tidyverse')
library('poppr')
library('viridis')
```

@@

>>>>

```{r load_packages}
library('igraph')
library('ggraph')
library('tidyverse')
library('poppr')
library('viridis')
library('visNetwork')
```

@@

### Interactive Visualizations

The *visNetwork* package wraps a java library that has very good network
visualization routines. I can conver this graph to that.

```{r}

make_rgb <- function(x, alpha = 1){
  out <- col2rgb(x, alpha = TRUE)
  out[4, ] <- floor(out[4, ]*alpha)
  out      <- apply(out, 2, paste, collapse = ", ")
  paste0("rgba(", out, ")")
}
vg <- g %>%
  set_vertex_attr("size", value = osize) %>%
  set_vertex_attr("value", value = osize) %>%
  set_vertex_attr("color", value = viridis(4)[as.integer(factor(the_communities$comm))]) %>%
  set_vertex_attr("shape", value = ifelse(V(.)$type == "Multilocus Genotype", "triangle", "circle")) %>%
  set_edge_attr("width", value = E(.)$weight) %>%
  toVisNetworkData()
vg$nodes <- vg$nodes %>% 
  group_by(id) %>%
  mutate(color = list(list(background = make_rgb(color, 0.8), 
                      border = make_rgb(rep("black", n()), 0.8),
                      highlight = list(background = make_rgb(color),
                                       border = make_rgb(rep("black", n()))
                                       )
                      )))
vgn <- visNetwork(nodes = vg$nodes, edges = vg$edges,# height = "500px", 
                  main = "Relation of Multilocus Genotypes and MCGs")
set.seed(2017-05-03)
vgn
# vgn %>%
#   visIgraphLayout("layout_nicely") %>%
#   visOptions(highlightNearest = list(enabled = TRUE, hover = TRUE), 
#              nodesIdSelection = TRUE)
#   
```
